Modular Deep Encoder-Decoders

### 2016-04-28 paper/draft.tex
insert figure for article-newspaper distribution

\section{Method}\label{method}
\subsection{Materials}
We used the freely available dataset from
\url{https://github.com/ParallelMazen/SaudiNewsNet} The dataset contains
a total of 31,030 Arabic newspaper articles. Article objects are reprensented in json
format, with UTF-8 encoding. We wrote a script to download the data from
github repo, unzip each file, and read them in as json objects. Each json object 
contains the flollowing fields:
source: A string identified of the newspaper from which the article was extracted. It can have one of the following values:
\begin{itemize}
\item source: A string identifier of the newspaper from which the article was extracted.
\item url: The full URL from which the article was extracted.
\item date\_extracted: The timestamp of the date on which the article was extracted. It has the format YYYY-MM-DD hh:mm:ss. 
\item title: The title of the article. 
\item author: The author of the article.
\item content: The content of the article.
\end{itemize}

>>>>

\section{Method}\label{method}
\subsection{Materials}
We used the freely available dataset from
\url{https://github.com/ParallelMazen/SaudiNewsNet} The dataset contains
a total of 31,030 Arabic newspaper articles, with a total number of 8,758,976 words.

\begin{figure}
\centering
\includegraphics[width=\textwidth]{figures/article-newspaper_distribution.png}
\caption{Figure shows article-newspaper distribution}
\end{figure}

Article objects are reprensented in json format, with UTF-8 encoding. We wrote a script to download the data from
github repo, unzip each file, and read them in as json objects. Each json object 
contains the flollowing fields:
source: A string identified of the newspaper from which the article was extracted. It can have one of the following values:
\begin{itemize}
\item source: A string identifier of the newspaper from which the article was extracted.
\item url: The full URL from which the article was extracted.
\item date\_extracted: The timestamp of the date on which the article was extracted. It has the format YYYY-MM-DD hh:mm:ss. 
\item title: The title of the article. 
\item author: The author of the article.
\item content: The content of the article.
\end{itemize}
